\cventry{2022}
    {News App}
    {-}
    {ReactJS}
    {}
    {Powered by \href{https://newsapi.org/}{\textcolor{blue}{NewsAPI}} public API, this app presents the latest news articles all around the world. The news are organized by categories on which user can click to view more articles. There are various categories users can browse such as entertainment, business, sports, technology, health, science and so on. Every article is composed of a title, description, author, publication date, and a channel of the article and a link to visit the source website. With responsive UI and UX, the whole smoothly adapts to different screen sizes and devices. Apart from react, I used \textbf{styled-components, react-bootstrap and axios library} to develop and \textbf{React Testing Library} to test this project. 
        \hfill
        \href{https://github.com/simranlotey/react-news-app.git}{\textcolor{blue}{\scriptsize Code}}
    }
    \vspace*{0.2\baselineskip}


\cventry{2021}
    {Currency Converter App}
    {-}
    {ReactJS}
    {}
    {This web application allows users to do currency conversions using \href{https://www.currencyconverterapi.com/}{\textcolor{blue}{CurrencyConverterApi}}. When the user loads the app, they are presented with a form where they can select the currency they want to convert from, the currency they want to convert to, and the amount they wish to convert. After clicking the button, the app calls the API to retrieve the current exchange rate for the selected currencies, and the converted amount. This app is developed with \textbf{Semantic UI React, Emotion} and tested with \textbf{React Testing Library}.
        \hfill
        \href{https://github.com/simranlotey/react-currency-converter.git}{\textcolor{blue}{\scriptsize Code}}
    }
    \vspace*{0.2\baselineskip}
